uncontrolled

### 2021-02-17 inst/examples/corporate.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/corporate_accepted.csv): `r length(unique(df$corporate))`
* [Unique discarded entries in original data](output.tables/corporate_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$corporate))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)

### 2021-02-17 inst/examples/holder.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/holder_accepted.csv): `r length(unique(df$holder))`
* [Unique discarded entries in original data](output.tables/holder_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)

### 2021-02-17 inst/examples/note_510c.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_510c))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/note_510c_accepted.csv): `r length(unique(df$note_510c))`
* [Unique discarded entries in original data](output.tables/note_510c_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_510c))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)

### 2021-02-17 inst/examples/note_dissertation.Rmd
change

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_dissertation))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)

>>>>

 * [Unique accepted entries](output.tables/note_disseration_accepted.csv): `r length(unique(df$note_dissertation))`
 * [Unique discarded entries in original data](output.tables/note_dissertation_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_dissertation_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_dissertation))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_dissertation)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_dissertation))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_dissertation)), 1)`%)

### 2021-02-17 inst/examples/note_granter.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/note_granter_accepted.csv): `r length(unique(df$note_granter))`
 * [Unique discarded entries in original data](output.tables/note_granter_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)

### 2021-02-17 inst/examples/note_source.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_source))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/note_source_accepted.csv): `r length(unique(df$note_source))`
* [Unique discarded entries in original data](output.tables/note_source_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_source_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_source))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_source)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_source))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_source)), 1)`%)

### 2021-02-17 inst/examples/subject_topic.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/subject_topic_accepted.csv): `r length(unique(df$subject_topic))`
* [Unique discarded entries in original data](output.tables/subject_topic_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)

### 2021-02-17 inst/examples/successor.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/succersor_accepted.csv): `r length(unique(df$title))`
* [Unique discarded entries in original data](output.tables/successor_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.tables, "/successor_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)

### 2021-02-17 inst/examples/title_uniform.Rmd
change

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)

>>>>

 * [Unique accepted entries](output.tables/title_uniform_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded entries in original data](output.tables/title_uniform_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_uniform_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)

### 2021-02-17 inst/examples/uncontrolled.Rmd
change

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$uncontrolled))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$uncontrolled))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$uncontrolled)), 1)`%)

>>>>

* [Unique accepted entries](output.tables/uncontrolled_accepted.csv): `r length(unique(df$uncontrolled))`
* [Unique discarded entries in original data](output.tables/uncontrolled_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$uncontrolled))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$uncontrolled)), 1)`%)
